Part B-1

### 2025-05-10 msca-pf-part-b1-template.tex
feat: make font 12pt like template and update tags

\documentclass[11pt,draftproposal]{msca-pf}
% {{{ packages

@@

\subsection{Quality and pertinence of the project's research and innovation objectives
    (and the extent to which they are ambitious, and go beyond the state of the art)}
    \mscatag{QUA-LIT-QL}
\label{ssc:excellence:quality}

@@

The schedule in the Gantt chart should indicate the number of months elapsed
from the start of the action (Month 1, Month 2, etc.) but no actual dates.

@@

\mscatagend{PRJ-MGT-PM} \mscatagend{CON-SOR-CS} \mscatagend{WRK-PLA-WP}
\mscatagend{QUA-LIT-QL}
\end{document}

>>>>

\documentclass[12pt,draftproposal]{msca-pf}
% {{{ packages

@@

\subsection{Quality and pertinence of the project's research and innovation objectives
    (and the extent to which they are ambitious, and go beyond the state of the art)}
\label{ssc:excellence:quality}

@@

The schedule in the Gantt chart should indicate the number of months elapsed
from the start of the action (Month 1, Month 2, etc.), but no actual dates.

@@

\mscatagend{CON-SOR-CS} \mscatagend{PRJ-MGT-PM} \mscatagend{QUA-LIT-QL} \mscatagend{WRK-PLA-WP}
\end{document}
